```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
#### reikiami paketai ir nustatymai

library(tidyverse)
library(readxl)
library(writexl)
library(DescTools)
library(ggpubr)
library(rstatix)
library(emmeans)
library(effectsize)
library(gtsummary)
library(broom)

```

-   mean CDA was extracted from the time window from 350 ms to 1000 ms

```{r}
# load the data

cda <- read_xlsx("avg_cda_condition.xlsx")

demographic <- read_xlsx("clean_demographic_questionnaires_hormones.xlsx")

age = demographic[c("id", "group", "age")]

head(cda)

```

**Remove Participants' Data**

```{r}
# Load the subject IDs from the text file into a vector
subjects_to_remove <- readLines("subjects_to_remove.txt", warn = FALSE)

# Convert the vector of strings to numeric
subjects_to_remove <- as.numeric(subjects_to_remove)

# Print the vector to confirm
print(subjects_to_remove)

```

```{r}


# Exclude subject's data
cda <- cda %>%
  filter(!id %in% subjects_to_remove)

# Remove male group
#cda <- cda[!(cda$group == "M"), ]

# Standardize all column names to lowercase
names(cda) <- tolower(names(cda))

# Convert columns to a factor and reorder levels
cda <- cda %>%
  mutate(group = factor(group, levels = c("NCF", "NCL", "OC", "IUD", "M")))

cda <- cda %>%
  mutate(stimuli_count = factor(stimuli_count, levels = c("3_stim", "4_stim")))

cda <- cda %>%
  mutate(hemisphere = factor(hemisphere, levels = c("left", "right")))

cda <- cda %>% convert_as_factor(id)

cda
```

```{r}
# Merge with age
cda <- merge(cda, age, by = c("id", "group"), all.x = TRUE)
cda
```

```{r}
# Define the desired order of levels
desired_order <- c( "M", "NCF", "NCL", "OC", "IUD")


convert_and_reorder <- function(df) {
  df$group <- factor(df$group, levels = desired_order)
  return(df)
}

cda <- convert_and_reorder(cda)

```

##Descriptive Statistics

**Mean and Median CDA amplitude by group, hemisphere and set size**

```{r}
print(cda %>% group_by(group, hemisphere, stimuli_count) %>% get_summary_stats(mean_cda, type = "median_iqr"))
```

```{r}
cda %>% group_by(group, hemisphere, stimuli_count) %>% get_summary_stats(mean_cda, type = "mean_sd")

```

**Mean CDA amplitude by hemisphere and set size**

```{r}
cda %>% group_by(hemisphere, stimuli_count) %>% get_summary_stats(mean_cda, type = "mean_sd")
```

**Visualizations**

```{r}

bxp_cda_hph_st <-
  ggboxplot(
    cda,
    x = "stimuli_count",
    y = "mean_cda",
    fill = "hemisphere",
    xlab = "Set size",
    legend.title = "Hemisphere",
    ylab = "Mean CDA (µV)"
  ) + scale_x_discrete(labels = c("3", "4")) + theme(legend.position = "top") + font("axis.title", size = 15) + font("legend.title", size = 14) + font("legend.text", size = 15) + font("xy.text", size = 15) + stat_summary(
    fun.y = mean,
    geom = "errorbar",
    aes(
      ymax = ..y..,
      ymin = ..y..,
      group = factor(hemisphere)
    ),
    width = 0.8,
    linetype = "dashed",
    position = position_dodge()
  )

bxp_cda_hph_st
```

**Mean CDA amplitude by hemisphere**

```{r}
cda %>% group_by(hemisphere) %>% get_summary_stats(mean_cda, type = "mean_sd")
```

```{r}
#grafikas

bxp_cda_hph <-
  ggboxplot(
    cda,
    x = "hemisphere",
    y = "mean_cda",
    xlab = "Hemisphere",
    ylab = "Mean CDA amplitude (µV)",
    width = 0.6) + scale_x_discrete(labels = c("Left", "Right")) + stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y.., group = factor(hemisphere)), width = 0.8, linetype = "dashed", position = position_dodge())
bxp_cda_hph
```

**Mean CDA amplitude by set size**

```{r}
#summary stats
cda %>% group_by(stimuli_count) %>% get_summary_stats(mean_cda, type = "mean_sd")
```

## **CHECK ASSUMPTIONS**

1.  **Linearity assumption**

```{r}
ggscatter(
  cda, x = "age", y = "mean_cda",
  color = "group", add = "reg.line"
  )+
  stat_regline_equation(
    aes(label =  paste(..eq.label.., ..rr.label.., sep = "~~~~"), color = group)
    )
```

2.  **Homogeneity of regression slopes**

```{r}

cda %>% anova_test(mean_cda ~ group * age)
```

3.  **Normality of residuals**

```{r}
cda |> 
  group_by(group, hemisphere, stimuli_count) |> 
  shapiro_test(mean_cda)
```

4.  **Homogeneity of variances**

```{r}
cda |>
  group_by(hemisphere, stimuli_count) |> 
  levene_test(mean_cda~group)
```

5.  **Outliers**

```{r}
cda |> 
group_by(group) |> 
identify_outliers(mean_cda)
```

**QQ plot**

```{r}
ggqqplot(cda, "mean_cda", ggtheme = theme_bw()) + facet_grid(stimuli_count ~ group*hemisphere)
```

Just in two cases parametricity assumption was little bit violated, therefore we can use parametric statistics


## mixed ANCOVA


```{r}
aov <- anova_test(data = cda, dv = mean_cda, wid = id,
  between = group, within = c(stimuli_count, hemisphere), covariate = age
  )
get_anova_table(aov)
```

```{r}

mean_cda <- ggplot(cda, aes(x = group, y = mean_cda, fill = group)) +
  geom_boxplot(width = 0.6, position = position_dodge(width = 0.8), color = "black", alpha = 0.7, outlier.shape = TRUE) + 
  labs(x = " ", y = "Mean CDA amplitude (µV)", fill = "Group") +
  scale_fill_manual(values = c("#0072B2", "#009E73", "#E69F00", "#999999", "#CC79A7")) +
  theme_classic() +
  theme(axis.text = element_text(size = 14, color = "black"), axis.title = element_text(size = 18, color = "black"),
        legend.position = "right", legend.title = element_text(size = 16), legend.text = element_text(size = 14)) 

# Print the plot
mean_cda
```

```{r}
ggsave("figures/mean_cda.png", mean_cda, width = 6, height = 4.5)
```
